---
title: "lab_02"
author: "Derek Willis"
adapted by: "Daniel Trielli"
date: "2024-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and establish settings

```{r}
# Turn off scientific notation
options(scipen=999)

# Load the tidyverse. If you have not installed the tidyverse already, remove the # from the next line and run it first.  
# install.packages('tidyverse')
library(tidyverse)
library(lubridate)
```

## Load Data

Let's keep working with the UMD courses and Maryland campaign expense data we used in the pre_lab.

```{r}
umd_courses <- read_rds("data/umd_courses.rds")
maryland_expenses <- read_csv("data/maryland_expenses.csv")
```

## Answer questions

### **Q1** How many departments have offered the courses with "Climate" in the title and at least one seat? Which department has offered the most?

```{r}
Climate <- umd_courses |>
  filter(str_detect(title, "Climate")) |>
  filter(seats >= 1) 

Climate |>
  group_by(department) |>
  summarise(
count_department = n()) |>

  arrange(desc(count_department))
```

**A1 26 departments offer courses with "Climate" in the title. The department which offers the most is Atmospheric and Oceanic Science with 68.**

------------------------------------------------------------------------

### **Q2** Which departments have the most courses in the Fall 2023 term? And which departments in that term have at least one syllabus posted? How are the top departments different in each result? Where is Journalism in those results?

```{r}
umd_courses |>
  filter(term == 202308) |>
  group_by(department) |>
    summarize(
      count_classes = n(),
    ) |>
  arrange(desc(count_classes)) 
  
umd_courses |>
  filter(syllabus_count > 0) |> filter(term == 202308) |>
  group_by(department) |>
  summarize(
    count_department = n()
  ) |>
  arrange(desc(count_department)) 
  

```

**A2 Business and Management has the most courses in the Fall 2023 term with 164, followed by School of Music with 137. Journalism is 6th with 110 courses. Business and management still has at least one syllabus posted, with 82 of their courses having syllabi. Economics is now second with 50 of their classes having syllabi. Journalism has been knocked down, now with only 12 classes with syllabi.**

------------------------------------------------------------------------

### **Q3** Using the Maryland campaign expenses data, change the datatype of the expenditure_date column so that it is a date and not a chr. 

### Then create a new column for the month based on expenditure_date. 

### Then write code that shows total amount spent each month by Wes Moore's committee (you'll need to search the data to find the exact name). 

### Write a sentence describing the pattern of spending over time.

```{r}
maryland_expenses <- read_csv("data/maryland_expenses.csv")

head(maryland_expenses)

maryland_expenses <- maryland_expenses |> mutate(expenditure_date=mdy(expenditure_date))

head(maryland_expenses)

maryland_expenses |>
  mutate(month = floor_date(expenditure_date, "month")) |>
  group_by(month) |>
  summarise(total_amount = sum(amount)) |>
  arrange(desc(total_amount))

```

**A3 It looks like the amount spent is going up as we get closer to a November election day. October 2022 has the most spent with 15827467.4, and November 2022 isn't very far behind in 4th place with 4715693.9. And if I'm right about it nearing election day, those funds wouldn't need to last the full month.**

------------------------------------------------------------------------

### **Q4** Using case_when(), create a column in the Maryland expenses data called `spending_location` indicating whether each record indicated money spent in Maryland or outside Maryland. For records that are in Maryland, make the new column's value "In-state" and for the others, make it "Out of state". Then write code that shows the total amount of money spent in each category and describe the results. You can do this in one statement or break it up into two statements (saving the new column to your dataframe).

```{r}
spending_location <- maryland_expenses |>
  mutate(
    state = case_when(
        str_detect(address, " Maryland ") ~ "in-state",
        str_detect(address, " California ") ~ "out",
        str_detect(address, " Washington ") ~ "out",
        str_detect(address, " Louisiana ") ~ "out",
        str_detect(address, " Florida ") ~ "out",
        str_detect(address, " North Carolina ") ~ "out",
        str_detect(address, " Massachusetts ") ~ "out",
        str_detect(address, " West Virginia ") ~ "out",
        str_detect(address, " Virginia ") ~ "out",
        .default = NA
      )
  )

spending_location |>
  group_by(state) |>
  summarize(total = sum(amount)) |>
  arrange(desc(total))
```

**A4 Money spent inside Maryland totals 77723146, money spent out of state totals 33164994. This is a difference of \$44,558,152, with more being spent within Maryland.**

------------------------------------------------------------------------

### **Q5** Choose your own adventure: using either the UMD courses or campaign expenses data, ask and answer a question that is different than the previous ones. You can use one of the ones you provided in the pre_lab.

We'll see if I can answer this question from my pre-lab:

1.  Where is the most out-of-state money going? Is it all one thing, like a federal grant? (I was confused when I wrote this, I'm just going to go with what is the most amount of money sorted into out-of-state...)

```{r}
spending_location <- maryland_expenses |>
  mutate(
    state = case_when(
        str_detect(address, " Maryland ") ~ "in-state",
        str_detect(address, " California ") ~ "out",
        str_detect(address, " Washington ") ~ "out",
        str_detect(address, " Louisiana ") ~ "out",
        str_detect(address, " Florida ") ~ "out",
        str_detect(address, " North Carolina ") ~ "out",
        str_detect(address, " Massachusetts ") ~ "out",
        str_detect(address, " West Virginia ") ~ "out",
        str_detect(address, " Virginia ") ~ "out",
        .default = NA
      )
  )


spending_location |>
group_by(state) |>
arrange(desc(amount)) 
```

**A5 9th down, a committee named Adams Tim(Timothy) gave \$422,500.00, and this is the biggest amount of money in the "out" (out-of-state) category under the expense category of "Media."**
