---
title: "Reverse Engineering Project Group 4"
author: "Josie Cat and Xavier "
date: "10/17"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this notebook, we are reverse engineering the story, **Inside The Political Donation History Of Wealthy Sports Owners**

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
options(scipen=999)
library(tidyverse)
library(janitor)
library(lubridate)
library(readr)
install.packages("dplyr")
library(dplyr)

```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data
sports <- read_csv("data/sports-political-donations.csv")

# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

sports_political_donations <- read_csv("data/sports-political-donations.csv") |>
  clean_names()
  
sports_political_donations <- sports_political_donations |>
  mutate(
   owner = str_to_upper(owner),
   team = str_to_upper(team),
   recipient = str_to_upper(recipient),
   party = str_to_upper(party),
   amount = gsub(",", "", amount),
   amount = gsub("\\$", "", amount),
   amount = as.double(amount)
  ) 
# Clean required data and prepare for analysis if needed. 
#as.double turns into number, which is the opposite of as.character 

```

"

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: **“A deep search in the Federal Election Commission database of campaign finances for principal owners, controlling owners, co-owners and commissioners from the NBA, NFL, NHL, WNBA, MLB and NASCAR reveals that this deep-pocketed group has sent \$34.2 million (72.9 percent) to Republican campaigns or super PACs purely supporting Republican causes, compared to \$10.1 million (21.5 percent) to Democrats over the past three elections.”**
-   **Analysis summary**: By grouping by party and then getting the sum of amounts given, we were then able to create a new block with the amounts and what party was giving them From there we got the percents of the total and were able to see that the Republican party donated the most with 72.89 percent, which was (fairly) rounded up to 72.9 percent in the article. We also see the correct 21.5 percent from democrats.
-   Note: I am unsure why my code does not show below, but the separate block should load and be view-able.

```{r}
# Put code to reverse engineer sentence here
#find which owners, co-owners, and comissioners from NBA, NFL, NHL, WNBA, MLB, NASCAR sent a total of $34.2 million to Republican campaigns 2024 in 2020 

sports_political_donations_amounts <- sports_political_donations |>
  group_by(party) |>
  summarise(
    party_amounts=sum(amount)
  )

sum(sports_political_donations_amounts$party_amounts)

sports_political_donations_amounts <- sports_political_donations_amounts |>
  mutate(
    pct_total=((party_amounts / (sum(sports_political_donations_amounts$party_amounts))) *100)
  ) |>
  arrange(desc(pct_total))


# Display results of code below this codeblock

sports_political_donations_amounts

#cat knew gsub and explained. she also explained the backslashes and that info is from chatgpt.

```

### Sentence 2

-   **Sentence text**: **“Forty owners account for more than \$40 million –**
-   **more than 85 percent of all contributions. And looking at these big spenders,**
-   **it’s clear where their allegiance lie: 77.7 percent of that \$40 million went to Republican causes or candidates, with 18.8 going to Democrats.”**
-   **Analysis summary**: First we gathered the top 40 contributors using top_n and arranged them by highest to lowest amount given. From there we added the 310 donations from those 40 people to determine if it was more than \$40 million.
-   it is 41 mil

```{r}
# find top 40 contributers/owners
# find the amount donated and which party that money goes to
# Put code to reverse engineer sentence here

top_40_owners <- sports_political_donations |>
  group_by(owner) |>
  summarise(donations = sum(amount)) |>
  top_n(40)
         
# Display results of code below this codeblock

(sum(top_40_owners$donations))/sum(sports_political_donations_amounts$party_amounts)

# find what percent these 40 are of all contributions

  

# Display results of code below this codeblock

```

```{r}
top_40_owners_list <- top_40_owners |>
  select(owner)

all_donors <- sports_political_donations |>
  group_by(owner, party) |>
  summarise(party_donations = sum(amount))

top_40_with_party <- top_40_owners_list |>
  left_join(all_donors)
  
top_40_with_party |>
  filter(party == "REPUBLICAN") |>
  summarise(sum(party_donations)) / (sum(top_40_owners$donations))

```

### Sentence 3

-   **Sentence text**: **“More than 63 percent of the \$47 million in the database of nearly 3,000 contributions comes from just 108 donations split among these 40 owners —**
-   **and 79 percent of that money went to Republican causes.”**
-   **Analysis summary**: First, we proved the 63 percent by getting the sum of the top 108 donors.

```{r}
# Put code to reverse engineer sentence here

top_40_all_donations <- sports_political_donations |>
  left_join(top_40_owners_list) |>
  arrange(desc(amount))

top_donations_from_top_40_owners <- top_40_all_donations |>
  head(108)

sum(top_donations_from_top_40_owners$amount)/sum(sports_political_donations$amount)*100

# result 

# 63.20321

top_donations_from_top_40_owners_by_party <- top_donations_from_top_40_owners |>
  group_by(party) |>
  summarise(party_amount=sum(amount)) |>
  filter(party=="REPUBLICAN")

top_donations_from_top_40_owners_by_party$party_amount/sum(top_donations_from_top_40_owners$amount)*100

# result

# 78.90937


```

### Sentence 4

-   **Sentence text**: **“Overall, 51.7 percent of all contributions by WNBA owners went to Democrats, with 42.3 percent going to Republicans. And of the \$1.3 million contributed by WNBA owners to Republicans, 65.5 percent comes from Kelly Loeffler, the Republican from Georgia who is co-owner of the Atlanta Dream.”**
-   **Analysis summary**: We created a new data set with top donations from the top 40 owners with parties included,

```{r}
# Put code to reverse engineer sentence here
# Put code to reverse engineer sentence here

wnba_contributions <- sports_political_donations |>
  filter(
    str_detect(league, "WNBA")
  )

wnba_contributions_by_party <- wnba_contributions |>
  group_by(party) |>
  summarise(total_amount=sum(amount)) |>
  arrange(desc(total_amount)) |>
  mutate(
    pct_total = total_amount/sum(total_amount)*100
  )

wnba_contributions_by_party |>
  select(party, pct_total) |>
  head(2)

# results

# 51.7% Democrat
# 42.3% Republican

wnba_republican_contributions <- wnba_contributions |>
  filter(party=="REPUBLICAN")

sum(wnba_republican_contributions$amount)

# result

# $1,338,459

wnba_republican_contributions_by_owner <- wnba_republican_contributions |>
  group_by(owner) |>
  summarise(total_amount = sum(amount))

wnba_republican_contributions_by_owner |>
  mutate(
    pct_total=total_amount/sum(total_amount)*100
  ) |>
  filter(owner == "KELLY LOEFFLER") |>
  select(owner, pct_total)

# result

# 65.5%

  
  #another data set, grouping by party and the sumarizing by sum of the amount and filter by republican
# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: **“Giants owner Charles Johnson’s total contributions make up 32.1% of the Republican contributions.”**
-   **Analysis summary**:

```{r}
republican_donations <- sports_political_donations |>
  filter(party=="REPUBLICAN")

charles_johnson_donations <- republican_donations |>
  filter(owner=="CHARLES JOHNSON")

sum(charles_johnson_donations$amount)/sum(republican_donations$amount)*100

# result

# 32.1%

```

-30-
